Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-18 analysis/paper/paper.Rmd
Added new source for methods regarding univariate k-means

  Finally, the shape landmark values were analysed by Principal Components Analysis, a form of exploratory data analysis. Our methodology for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. PCA

  PCA biplots were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components were then used to create biplots comparing the shape data to the flake reduction categories, excavation unit, and mass clusters, with the secondary variables being represented by colored outlines on the biplots.

@@

@@

@@

>>>>

  Finally, the shape landmark values were analysed by Principal Components Analysis, a form of exploratory data analysis. Our methodology for carrying out the PCA on the shape landmarks was inspired by Theska et al. (2020), which also performed 2D landmark data analysis using PCA. Principal Component Analysis takes the initial set of data and transforms the initial set of variables into a smaller set of variables whist still preserving most of the variation seen in the initial data set. PCA biplots, which plot out the first two primary components, were created to visualize differences based upon secondary categorical variables, namely flake reduction categories, excavation unit, and mass cluster. The first two primary components formulated the individual points on biplot, while the secondary variables (flake reduction categories, excavation unit, and mass clusters) were represented by colored outlines on the biplots

@@

<!-- QH: Added more information on GPA and PCA, as well as an addition citation -->

@@

Papageorgiou (2020)

@@

Papageorgiou, I. (2020). Ceramic investigation: How to perform statistical analyses. Archaeological and Anthropological Sciences, 12(9), 210. https://doi.org/10.1007/s12520-020-01142-x
